### 2022-03-28 manuscript.tex
Update default.docx [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/955268d80bc836362cda9439625643593e01e1a7.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/955268d80bc836362cda9439625643593e01e1a7/checks
https://github.com/scherzerthesis/thesis/actions/runs/2053330414

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/c0eb8807f43cb1cfa23b023bee6fccf181e816ec/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/c0eb8807f43cb1cfa23b023bee6fccf181e816ec}{scherzerthesis/thesis@c0eb880}
on March 28, 2022.

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/955268d80bc836362cda9439625643593e01e1a7/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/955268d80bc836362cda9439625643593e01e1a7}{scherzerthesis/thesis@955268d}
on March 28, 2022.
